CLT Results

### 2022-04-13 analysis/clt_data_processing.Rmd
add gafor merge and item selection files

```{r}
dem <- bind_rows(
  read_xlsx("../../../../Cloud/Shared/CLT_Kinderlisten_fuer_Emailversandt_14032022.xlsx", sheet = 1),
  read_xlsx("../../../../Cloud/Shared/CLT_Kinderlisten_fuer_Emailversandt_14032022.xlsx", sheet = 2),
  read_xlsx("../../../../Cloud/Shared/CLT_Kinderlisten_fuer_Emailversandt_14032022.xlsx", sheet = 3),
  read_xlsx("../../../../Cloud/Shared/CLT_Kinderlisten_fuer_Emailversandt_14032022.xlsx", sheet = 4),
  read_xlsx("../../../../Cloud/Shared/CLT_Kinderlisten_fuer_Emailversandt_14032022.xlsx", sheet = 5),
  read_xlsx("../../../../Cloud/Shared/CLT_Kinderlisten_fuer_Emailversandt_14032022.xlsx", sheet = 7),
  read_xlsx("../../../../Cloud/Shared/CLT_Kinderlisten_fuer_Emailversandt_14032022.xlsx", sheet = 10),
  read_xlsx("../../../../Cloud/Shared/CLT_Kinderlisten_fuer_Emailversandt_14032022.xlsx", sheet = 12)
  )%>%
  select(code,g,`geb.tag`)%>%
  rename(subjID = "code", birth_day = "geb.tag", sex = "g")%>%
  mutate(birth_day = as.Date(birth_day, "%d.%m.%Y"),
         sex = ifelse(sex == "w","f","m"))%>%
  add_row(subjID = "leon", sex = "m", birth_day = as.Date("2015-09-03","%Y-%m-%d"))%>%
  add_row(subjID = "joshi", sex = "m", birth_day = as.Date("2017-06-01","%Y-%m-%d"))%>%
  distinct(subjID,.keep_all = T)

@@

```{r}
dem%>%
  group_by(subjID)%>%
  summarise(n=n())%>%
  filter(n >1)

@@

```{r}
data <- bind_rows(
  data_mpi%>%mutate(source = "mpi", postcode = "04103"),
  #data_zas%>%mutate(source = "zas_kischawi")
)
```

@@

ggplot(p1_2, aes(x = mean_orderA, y = mean_orderB))+
  stat_cor(aes(label = paste(..r.label..)),r.accuracy = 0.01, cor.coef.name = "r")+
  geom_abline(intercept = 0, slope = 1, lty = 3, alpha = .75)+
  geom_textpath(aes(label = german), hjust = -.2) +
  #geom_hline(yintercept = 0.25, alpha = .5)+
  #geom_vline(xintercept = 0.25, alpha = .5)+
  geom_errorbar(aes(xmin = ci_lower_orderA, xmax = ci_upper_orderA), alpha = .5)+
  geom_errorbar(aes(ymin = ci_lower_orderB, ymax = ci_upper_orderB), alpha = .5)+
  geom_point( size =2, stroke = 1, alpha= .75)+
  labs(x = "Order A", y = "Order B")+
  ylim(0,1)+
  xlim(0,1)+
  theme_minimal()
```

>>>>

```{r}
dem <- bind_rows(
  read_xlsx("../../../../Cloud/Shared/CLT_Kinderlisten_fuer_Emailversandt_14032022.xlsx", sheet = 1),
  read_xlsx("../../../../Cloud/Shared/CLT_Kinderlisten_fuer_Emailversandt_14032022.xlsx", sheet = 2),
  read_xlsx("../../../../Cloud/Shared/CLT_Kinderlisten_fuer_Emailversandt_14032022.xlsx", sheet = 3),
  read_xlsx("../../../../Cloud/Shared/CLT_Kinderlisten_fuer_Emailversandt_14032022.xlsx", sheet = 4),
  read_xlsx("../../../../Cloud/Shared/CLT_Kinderlisten_fuer_Emailversandt_14032022.xlsx", sheet = 5),
  read_xlsx("../../../../Cloud/Shared/CLT_Kinderlisten_fuer_Emailversandt_14032022.xlsx", sheet = 7),
  read_xlsx("../../../../Cloud/Shared/CLT_Kinderlisten_fuer_Emailversandt_14032022.xlsx", sheet = 10),
  read_xlsx("../../../../Cloud/Shared/CLT_Kinderlisten_fuer_Emailversandt_14032022.xlsx", sheet = 11),
  read_xlsx("../../../../Cloud/Shared/CLT_Kinderlisten_fuer_Emailversandt_14032022.xlsx", sheet = 12),
  read_xlsx("../../../../Cloud/Shared/CLT_Kinderlisten_fuer_Emailversandt_14032022.xlsx", sheet = 13),
  read_xlsx("../../../../Cloud/Shared/CLT_Kinderlisten_fuer_Emailversandt_14032022.xlsx", sheet = 14)
  )%>%
  select(code,g,`geb.tag`)%>%
  rename(subjID = "code", birth_day = "geb.tag", sex = "g")%>%
  mutate(birth_day = as.Date(birth_day, "%d.%m.%Y"),
         sex = ifelse(sex == "w","f","m"))%>%
  add_row(subjID = "leon", sex = "m", birth_day = as.Date("2015-09-03","%Y-%m-%d"))%>%
  add_row(subjID = "joshi", sex = "m", birth_day = as.Date("2017-06-01","%Y-%m-%d"))%>%
  distinct(subjID,.keep_all = T)

@@

```{r}
# dem%>%
#   group_by(subjID)%>%
#   summarise(n=n())%>%
#   filter(n >1)

@@

```{r}
data <- bind_rows(
  data_mpi%>%mutate(source = "mpi", postcode = "04103"),
  data_zas%>%mutate(source = "zas_kischawi")
)
```

@@

ggplot(p1_2, aes(x = mean_orderA, y = mean_orderB))+
  stat_cor(aes(label = paste(..r.label..)),r.accuracy = 0.01, cor.coef.name = "r")+
  geom_abline(intercept = 0, slope = 1, lty = 3, alpha = .75)+
  #geom_textpath(aes(label = german), hjust = -.2) +
  #geom_hline(yintercept = 0.25, alpha = .5)+
  #geom_vline(xintercept = 0.25, alpha = .5)+
  geom_errorbar(aes(xmin = ci_lower_orderA, xmax = ci_upper_orderA), alpha = .5)+
  geom_errorbar(aes(ymin = ci_lower_orderB, ymax = ci_upper_orderB), alpha = .5)+
  geom_point( size =2, stroke = 1, alpha= .75)+
  labs(x = "Order A", y = "Order B")+
  ylim(0,1)+
  xlim(0,1)+
  theme_minimal()
```

### 2022-04-13 analysis/clt_irt_analysis.Rmd
add gafor merge and item selection files

```{r}
params%>%left_join(coefs2PL)%>%
  mutate(slope = ifelse(nlpar == "Easiness", -1,1))%>%
  ggplot(aes(x = Estimate, y = par))+
  geom_abline(aes(slope = slope, intercept = 0), lty = 3, alpha = .5)+
  geom_errorbar(aes(ymin = CI_2.5, ymax = CI_97.5), alpha = .25, col = "dodgerblue")+
  geom_errorbarh(aes(xmin = Q2.5, xmax = Q97.5), alpha = .25, col = "dodgerblue")+
  geom_point(pch = 1, alpha = .75)+
  facet_grid(~nlpar)+
  labs(x = "Bayesian estimate", y = "Frequentist estimate")+
  stat_cor()+
  ylim(-10,10)+
  xlim(-10,10)+
  #coord_fixed(ratio = 1)+
  scale_color_viridis_c()+
  theme_bw()
```
# Correlation subtest and full test

```{r}
select <-params %>%
  pivot_wider(names_from = nlpar, values_from = Estimate)%>%
  arrange(
    Easiness, 
    #-Discrimination
    )%>%
  slice(1:15)%>%
  pull("item")

full <- data%>%
  group_by(age_group,subjID)%>%
  summarise(mean_full = mean(correct))

sub <- data%>%
  filter(targetWord %in% select)%>%
  group_by(age_group,subjID)%>%
  summarise(mean_sub = mean(correct))

comp <- full%>%left_join(sub)

ggplot(comp, aes(x = mean_full, y = mean_sub))+
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = .75)+
  geom_jitter(pch = 1, alpha = .75, height = 0.01, width = 0.01)+
  stat_cor()+
  facet_wrap(~age_group)+
  ylim(0,1.02)+
  xlim(0,1.02)+
  theme_few()

dat <- tibble(
  iter = c(),
  items = c(),
  cor = c(),
)

full <- data%>%
  group_by(subjID)%>%
  summarise(mean_full = mean(correct))

for (i in 1:200) {

  items <-params %>% pull("item")

  sel_items <- sample(items, 15)

  sub <- data%>%
  filter(targetWord %in% sel_items)%>%
  group_by(subjID)%>%
  summarise(mean_sub = mean(correct))

  cor <- cor(full$mean_full,sub$mean_sub)

  df <- tibble(
    iter = i,
    items = sel_items,
    cor = cor
  )

  dat <- bind_rows(dat,df)

}

dat%>%
  group_by(items)%>%
  summarise(mean_cor = mean(cor))%>%
  arrange(-mean_cor)

full <- data%>%
  group_by(age_group,subjID)%>%
  summarise(mean_full = mean(correct))

select2 <- dat%>%group_by(items)%>%
  summarise(mean_cor = mean(cor))%>%
  arrange(-mean_cor)%>%slice(1:15)%>%pull(items)

sub2 <- data%>%
  filter(targetWord %in% select2)%>%
  group_by(age_group,subjID)%>%
  summarise(mean_sub = mean(correct))

comp2<- full%>%left_join(sub2)

ggplot(comp2, aes(x = mean_full, y = mean_sub))+
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = .75)+
  geom_jitter(pch = 1, alpha = .75, height = 0.01, width = 0.01)+
  stat_cor()+
  facet_wrap(~age_group)+
  ylim(0,1.02)+
  xlim(0,1.02)+
  theme_few()

>>>>

```{r}
params%>%left_join(coefs2PL)%>%
  mutate(slope = ifelse(nlpar == "Easiness", -1,1))%>%
  ggplot(aes(x = Estimate, y = par))+
  geom_abline(aes(slope = slope, intercept = 0), lty = 3, alpha = .5)+
  geom_errorbar(aes(ymin = CI_2.5, ymax = CI_97.5), alpha = .25, col = "dodgerblue")+
  geom_errorbarh(aes(xmin = Q2.5, xmax = Q97.5), alpha = .25, col = "dodgerblue")+
  geom_point(pch = 1, alpha = .75)+
  facet_grid(~nlpar)+
  labs(x = "Bayesian estimate", y = "Frequentist estimate")+
  stat_cor()+
  ylim(-10,10)+
  xlim(-10,10)+
  #coord_fixed(ratio = 1)+
  scale_color_viridis_c()+
  theme_bw()
```
